Brownian Dynein Model

### 2015-09-16 latex/derivation.tex
Make preparations for bothbound solution.
Add beginnings of bothbound derivation

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{b1} &= ?? \\
  X_{m1} &= ?? \\
  X_{t}  &= ?? \\
  X_{m2} &= ?? \\
  X_{b2} &= ??
\end{align}

\begin{align}
  Y_{b1} &= ?? \\
  Y_{m1} &= ?? \\
  Y_{t}  &= ?? \\
  Y_{m2} &= ?? \\
  Y_{b2} &= ??
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{b1} &= ?? \\
  \dot{X}_{m1} &= ?? \\
  \dot{X}_{t } &= ?? \\
  \dot{X}_{m2} &= ?? \\
  \dot{X}_{b2} &= ??
\end{align}

\begin{align}                                                                          
  \dot{Y}_{b1} &= ?? \\                                                        
  \dot{Y}_{m1} &= ?? \\
  \dot{Y}_{t}  &= ?? \\
  \dot{Y}_{m2} &= ?? \\
  \dot{Y}_{b2} &= ?? \\
\end{align}

\section{Cartesian Velocities (expanded)}
This section expands the above definitions. \\
\begin{align}
  \dot{X}_{b1} &= ?? \\
  \dot{X}_{m1} &= ?? \\
  \dot{X}_{t } &= ?? \\
  \dot{X}_{m2} &= ?? \\
  \dot{X}_{b2} &= ?? \\
\end{align}

\begin{align}                                                                               
  \dot{Y}_{b1} &= ?? \\
  \dot{Y}_{m1} &= ?? \\
  \dot{Y}_{t}  &= ?? \\
  \dot{Y}_{m2} &= ?? \\
  \dot{Y}_{b2} &= ?? \\
\end{align}

>>>>

\begin{figure}[h!]
  \caption{Key lengths and angles in bothbound dynein model.}
  \centering
    \includegraphics[width=0.7\textwidth]{../figures/bothbound_model.png}
\end{figure}

\section{Cartesian Coordinate Derivation}

By the law of cosines:
\begin{align}
  L_n &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})}\\
  L_f &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{fm})}\\
\end{align}

Also by the law of cosines, we see that:
\begin{align}
  \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
  \Theta_{2} &= \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
\end{align}

We use these equations to solve for our nm (near motor) coordinates:

\begin{align}
  X_{nm} &= L_{s}*\cos(\Theta_{1}+\Theta_{2}) =
     L_{s}*\cos\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
     + \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
  Y_{nm} &= L_{s}*\sin(\Theta_{1}+\Theta_{2}) =
     L_{s}*\sin\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
     + \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
\end{align}

We then use the trigonometric rules $$\cos\Big(cos^{-1}(a)+cos^{-1}(b)\Big) = ab - \sqrt{1-a^2}\sqrt{1-b^2}$$ and $$\sin\Big(cos^{-1}(a)+cos^{-1}(b)\Big) = \sqrt{1-a^2}b+a\sqrt{1-b^2}$$ to simplify our expressions:

\begin{align}
  X_{nm} &= L_{s}*((\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}) - \sqrt{1-(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})^2}\sqrt{1-(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})^2}) \\
  Y_{nm} &= L_{s}*(\sqrt{1-(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})^2}(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})+(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})\sqrt{1-(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})^2}) \\
\end{align}

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{b1} &= 0 \\
  X_{m1} &= L_{s}*\cos(\Theta_{b1}) \\
  X_{t}  &= ?? \\
  X_{m2} &= L_{s}*\cos(\Theta_{b2}) \\
  X_{b2} &= L \\
\end{align}

\begin{align}
  Y_{b1} &= 0 \\
  Y_{m1} &= L_{s}*\sin(\Theta_{b1}) \\
  Y_{t}  &= ?? \\
  Y_{m2} &= L_{s}*\sin(\Theta_{b2}) \\
  Y_{b2} &= 0
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{b1} &= 0 \\
  \dot{X}_{m1} &= -L_{s}*\sin(\Theta_{b1})*\dot{\Theta}_{b1} \\
  \dot{X}_{t } &= ?? \\
  \dot{X}_{m2} &= -L_{s}*\sin(\Theta_{b2})*\dot{\Theta}_{b2} \\
  \dot{X}_{b2} &= 0
\end{align}

\begin{align}                                                                          
  \dot{Y}_{b1} &= 0 \\                                         
  \dot{Y}_{m1} &= L_{s}*\cos(\Theta_{b1})*\dot{\Theta}_{b1} \\
  \dot{Y}_{t}  &= ?? \\
  \dot{Y}_{m2} &= L_{s}*\cos(\Theta_{b2})*\dot{\Theta}_{b2} \\
  \dot{Y}_{b2} &= 0 \\
\end{align}
